% TODO Add title, student first/last name, supervisor first/last name.

\section*{Intellectual Property Agreement}

%\vspace{1cm}
%\subsection*{Preamble}

The student acted under the supervision of Prof. Hutter and contributed to research of his group.
Research results of students outside the scope of an employment contract with ETH Zurich belong to the students themselves.
The results of the student within the present thesis shall be exploited by ETH Zurich, possibly together with results of other contributors in the same field.
To facilitate and to enable a common exploitation of all combined research results, the student hereby assigns his rights to the research results to ETH Zurich.
In exchange, the student shall be treated like an employee of ETH Zurich with respect to any income generated due to the research results.

This agreement regulates the rights to the created research results.



\subsubsection*{1. Intellectual Property Rights} 

\begin{enumerate}[topsep=0pt,itemsep=0ex,partopsep=1ex,parsep=1ex]
\item The student assigns his/her rights to the research results, including inventions and works protected by copyright, but not including his moral rights (“Urheberpers\"onlichkeitsrechte”), to ETH Zurich. Herewith, he cedes, in particular, all rights for commercial exploitations of research results to ETH Zurich. He is doing this voluntarily and with full awareness, in order to facilitate the commercial exploitation of the created Research Results. The student's moral rights (“Urheberpers\"onlichkeitsrechte”) shall not be affected by this assignment.

\item	In exchange, the student will be compensated by ETH Zurich in the case of income through the commercial exploitation of research results. Compensation will be made as if the student was an employee of ETH Zurich and according to the guidelines  \href{https://rechtssammlung.sp.ethz.ch/Dokumente/440.4.pdf?Web=1}{“Richtlinien f\"ur die wirtschaftliche Verwertung von Forschungsergebnissen der ETH Z\"urich”}.

\item	The student agrees to keep all research results confidential. This obligation to confidentiality shall persist until he or she is informed by ETH Zurich that the intellectual property rights to the research results have been protected through patent applications or other adequate measures or that no protection is sought, but not longer than 12 months after the collaborator has signed this agreement.

\item If a patent application is filed for an invention based on the research results, the student will duly provide all necessary signatures. He/she also agrees to be available whenever his aid is necessary in the course of the patent application process, e.g. to respond to questions of patent examiners or the like. 

\end{enumerate}

\subsubsection*{2. Settlement of Disagreements}

Should disagreements arise out between the parties, the parties will make an effort to settle them between them in good faith.
In case of failure of these agreements, Swiss Law shall be applied and the Courts of Zurich shall have exclusive jurisdiction.



\vspace{3cm}

\begin{tabular}{ p{5cm} p{1cm} p{5cm} }
  \cline{1-1} \cline{3-3}
  Place and date & & Signature \\
\end{tabular}
